\RequirePackage{pdf14}
\documentclass[pdfa]{drdc-report}
\usepackage{drdc-docctl}
\usepackage{drdc-rtf-abstract}
\usepackage{drdc-submission}

% Use T1 fonts for correct French hyphenation
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\renewcommand\sfdefault{phv}
\usepackage{glossaries}
\usepackage{amsbsy}
\usepackage{amsmath}
\usepackage{amsthm}
% \ifx\pdftexversion\undefined
%   \usepackage[dvips]{graphicx}
% \else
%   \usepackage[pdftex]{graphicx,hyperref}
%   \hypersetup{backref,colorlinks=true,plainpages=false,pdfpagelabels}
%   \hypersetup{%
%     colorlinks=true,   % aktiviert farbige Referenzen
%     linkcolor=black,    % Make the link colours blue
%     citecolor=black,
%     filecolor=black,
%     pdfpagemode=UseNone,  % PDF-Viewer startet ohne Inhaltsverzeichnis et.al.
%     pdfstartview=FitH} % PDF-Viewer benutzt beim Start bestimmte Seitenbreite
%   
%   \hypersetup{% Ä=\304; Ö=\326; Ü=\334; ä=\344; ö=\366; ü=\374; ß=\377
%     pdftitle={Wavenumber domain representation of satellite signal},
%     pdfauthor={Ishuwa C. Sikaneta},
%     pdfsubject={Special Functions},
%     pdfkeywords={Statistics, Product model, Stationarity, Gaussian, Non Gaussian, SAR, GMTI, CFAR}
%   }
% \fi
% \usepackage[x11names, svgnames, rgb]{xcolor}
%\usepackage[utf8]{inputenc}
\usepackage{tikz}
\usepackage{pgfplots}
\usetikzlibrary{snakes,arrows,shapes}

\usepackage[mathscr]{euscript}
\usepackage{subcaption}
\usepackage{dblfloatfix}
\usepackage{fixltx2e}
\usepackage{color}
\usepackage{array, hhline}
\usepackage[normalem]{ulem}
\usepackage{rotating}
\usepackage{marvosym}
\usepackage{multirow}
\usepackage[mathscr]{euscript}
\usepackage{listings}
% \definecolor{gray}{rgb}{0.4,0.4,0.4}
% \definecolor{darkblue}{rgb}{0.0,0.0,0.6}
% \definecolor{cyan}{rgb}{0.0,0.6,0.6}
% \definecolor{Brown}{cmyk}{0,0.81,1,0.60}
% \definecolor{OliveGreen}{cmyk}{0.64,0,0.95,0.40}
% \definecolor{CadetBlue}{cmyk}{0.62,0.57,0.23,0}

\definecolor{lightlightgray}{gray}{0.9}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\definecolor{gray}{rgb}{0.4,0.4,0.4}
\definecolor{darkblue}{rgb}{0.0,0.0,0.6}
\definecolor{lightblue}{rgb}{0.0,0.0,0.9}
\definecolor{cyan}{rgb}{0.0,0.6,0.6}
\definecolor{darkred}{rgb}{0.6,0.0,0.0}


\lstset{
  basicstyle=\ttfamily\footnotesize,
  columns=fullflexible,
  showstringspaces=false,
  numbers=left,                                % where to put the line-numbers
  numberstyle=\tiny\color{gray},               % the style that is used for the line-numbers
  stepnumber=1,
  numbersep=5pt,                               % how far the line-numbers are from the code
  backgroundcolor=\color{lightlightgray},      % choose the background color. You must add \usepackage{color}
  showspaces=false,                            % show spaces adding particular underscores
  showstringspaces=false,                      % underline spaces within strings
  showtabs=false,                              % show tabs within strings adding particular underscores
  frame=none,                                  % adds a frame around the code
  rulecolor=\color{black},                     % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. commens (green here))
  tabsize=2,                                   % sets default tabsize to 2 spaces
  captionpos=b,                                % sets the caption-position to bottom
  breaklines=true,                             % sets automatic line breaking
  breakatwhitespace=false,                     % sets if automatic breaks should only happen at whitespace
  title=\lstname,                              % show the filename of files included with \lstinputlisting;
                                               % also try caption instead of title  
  commentstyle=\color{gray}\upshape
}


\lstdefinelanguage{XML}
{
  morestring=[s][\color{mauve}]{"}{"},
  morestring=[s][\color{black}]{>}{<},
  morecomment=[s]{<?}{?>},
  morecomment=[s][\color{dkgreen}]{<!--}{-->},
  stringstyle=\color{black},
  identifierstyle=\color{lightblue},
  keywordstyle=\color{red},
  morekeywords={xmlns,xsi,noNamespaceSchemaLocation,type,id,x,y,source,target,version,tool,transRef,roleRef,objective,eventually}% list your attributes here
}


%\usepackage[bibstyle=nature, style=drdc, citestyle=numeric-comp, sorting=none, backend=bibtex]{biblatex}
%\usepackage[bibstyle=nature, style=numeric, citestyle=numeric-comp, sorting=none, backend=bibtex]{biblatex}
%\bibliography{C:/Users/Ishuwa.Sikaneta/Documents/Legacy/bibliography/ishbib}
%\usepackage[style=numeric, citestyle=numeric-comp, sorting=none, backend=biber]{biblatex}%
%\bibliography{/home/ishuwa/Documents/bibliography/ishbib}

% Load hyperref
\definecolor{navy}{rgb}{0,0,0.5}
\definecolor{Maroon}{rgb}{0.6836,0.1953,0.2070}
\newcommand\mydriver{\ifpdf pdftex\else dvips,breaklinks\fi}
\usepackage[\mydriver,draft=false,plainpages=false,
    colorlinks=true,linkcolor=navy,anchorcolor=navy,citecolor=navy,
    filecolor=navy,urlcolor=navy,raiselinks=true,
    bookmarksnumbered=true]{hyperref}

\newcommand\mytitle{Super Resolution Synthetic Aperture Radar}
\title{\mytitle}
\subtitle{Design and Signal Processing of a Multi-Beam Multi-Channel Stripmap Mode}
\docnumber{---Will be inserted by Publication Officer}
\establishment{\DRDCO}
%\author{C.H.~Gierull}
\author{I.C. Sikaneta}
\authors{I.C.~Sikaneta[International Atomic Energy Agency - Vienna]
         C.H.~Gierull[\establishmentname]%
         }

% These definitions are used by drdc-docctl.sty
\projectnumber{42zz78}
\addkeyword{SAR}
\addkeyword{HRWS}
\addkeyword{Multi-channel}
\addkeyword{Orbit}
\addkeyword{Differential geometry}
\addkeyword{Multi-beam}
\addkeyword{Spherical harmonics}
\addkeyword{High-resolution}
\addkeyword{Phased-array}
\addkeyword{True time-delay}
\addkeyword{Spotlight}

% Pass title, author and keywords to hyperref to put in the PDF Info.
\makeinitializedauthors\mypdfauthors{; }
\makeexpandedkeywords\mypdfkeywords{; }
\hypersetup{
  pdftitle={\mytitle},
  pdfauthor={\mypdfauthors},
  pdfkeywords={\mypdfkeywords}
}
\futuredistribution{Defence departments and their contractors}{None}

%Public release
%Defence departments
%Defence departments and their contractors
%Government departments/agencies
%Government departments/agencies and their contractors
%Further distribution done by approval from Defence Research and Development Canada’s Authority

%\distribution
\input{ishCommands}
\input{myGlossary}
\DeclareUnicodeCharacter{2212}{-}
\pgfplotsset{compat=1.16}

\begin{document}

% Add the cover page
\makefrontcover

\begin{abstract}
By presenting the design, configuration and required end-to-end signal processing, this report proposes a system for improved \Index{\gls{sar}} imaging. Compared to conventional Spotlight \gls{sar}, the proposed system will generate imagery with equivalent or better resolution and significantly increased area coverage. The design and configuration are based upon a phased-array antenna in combination with the appropriate hardware to enable rapid electronic beam steering and to permit digitisation of multiple receive channels. The current state of technology is mature enough to construct all components of such a system. As a specific goal, the report proposes a system capable of imaging with 10 cm resolution (azimuth and slant-range) over a ground swath of 5 km. The proposed system is simulated at X-band, but could, in principle, be operated at any band with sufficiently available bandwidth. Importantly, this mode can collect with unlimited azimuth extent, something that no other proposed system can achieve.
\par
As the considered resolutions push the limits of known theory, the report also introduces an augmented theory that is needed to derive the signal processing algorithms. The presented approach incorporates a physical model, based upon the spherical harmonic model of the Earth's gravitational potential, into the theory of differential geometry of curves in three dimensions. From the theory, a wavenumber-based \gls{sar} processing algorithm that extends current methods is developed and presented. The proposed algorithm relies only on accurate attitude data and a single accurate state vector. The approach is therefore suitable for on-board SAR processing if sensor instruments can measure these parameters while imaging.
\end{abstract}

\begin{significance}
The material presented in this report provides the design and signal-processing framework for a \gls{sar} that can image with extremely high resolutions over wide areas. This capability does not exist for current systems, nor will it be possible with future systems, as currently planned. On the one hand, the novel proposed design offers improved SAR imaging without giving up any of the capabilities currently offered by national assets. On the other hand, the improvements meet or exceed current capability gaps in C4ISR requirements. The design (or some variant thereof) should be considered for future \gls{sar} missions.
\end{significance}

\begin{fabstract}
  Ceci est le r\'esum\'e en fran\c{c}ais.
\end{fabstract}

\begin{fsignificance}
  Ceci est l'importance pour la d\'efense et la s\'ecurit\'e.
\end{fsignificance}

\tableofcontents\clearpage
\listoffigures\clearpage
\listoftables
\begin{acknowledgements}
The authors would like to thank the Technical University of Vienna for granting permission to use the Vienna Super Computing (VSC) cluster. Without this resource, the simulations could not have been pushed to the limit of 10 cm resolution.
\end{acknowledgements}
\let\cleardoublepage\clearpage
\input{SURE_introduction}
\input{multichannelmodel}
% \chapter{System configuration}
\input{SURE_multichannel}
\input{SURE_transmit}
% \chapter{Signal collection geometry}
\input{orbiterror}
\input{diffgeo}
\input{diffgeoslow}
\input{diffgeostategeoid}
\input{orbit_demo}
\input{range}
% \chapter{Single channel measured signal}
\input{sardiffgeo}
\input{demodulation}
% \chapter{Wavenumber processing}
\input{stationaryphase}
\input{newStationaryPhase}
\input{antennaangles}
% \chapter{Signal processing of multichannel signals}
\input{introduction}
\input{multichannel}
% \chapter{End-to-end simulation}
\input{simulation}
\input{conclusion}

% Add the References section
\clearpage
\bibliographystyle{drdc}
\newcommand{\pauthor}[1]{#1}
\begin{thebibliography}{10}
\makeatletter
\@ifundefined{url}{
  \def\url{\begingroup\catcode`\~=12\catcode`\_=12%
           \deactivatepunctuation\DRDC@url}
  \def\DRDC@url#1{\texttt{#1}\endgroup}}{}
\ifDRDC@isfrench
  \def\in{dans}\def\In{Dans}\def\of{de}\def\and{et}
  \def\online{en~ligne}\def\accessdate{Date d'acc\`es}
  \def\masters{th\`ese de Ma\^itrise}\def\phd{th\`ese de Doctorat}
\else
  \def\in{in}\def\In{In}\def\of{of}\def\and{and}
  \def\online{online}\def\accessdate{Access Date}
  \def\masters{Master's thesis}\def\phd{Ph.D.\ thesis}
\fi
\ifDRDC@isclassified\else\def\U{}\fi
\makeatother

\bibitem{SentinelPOD}
\U European Space Agency, {Copernicus Sentinels POD Data Hub}.
\newblock https://scihub.copernicus.eu/gnss/\#/home.

\bibitem{GFZ}
\U Helmholtz Centre Potsdam, {Information System and Data Center for geoscientific data}.
\newblock http://isdc-old.gfz-potsdam.de/.

\bibitem{Brautigam2010}
\U Br{\"a}utigam,~B., Rizzoli,~P., Gonzalez,~C., Weigt,~M., Schrank,~D.,
  Schulze,~D., \and\ Schwerdt,~M. (2010), {SAR performance monitoring for
  TerraSAR-X mission}, \In\ {\em {Geoscience and Remote Sensing Symposium
  (IGARSS), 2010 IEEE International}}, pp.~3454--3457.

\bibitem{Fox2004}
\U Fox,~P.~A., Luscombe,~A.~P., \and\ Thompson,~A.~A. (2004), {{RADARSAT-2
  {SAR}} modes development and utilization}, {\em Canadian journal of remote
  sensing}, 30(3), 258--264.

\bibitem{Porfilio2016}
\U Porfilio,~M., Serva,~S., Fiorentino,~C. A.~M., \and\ Calabrese,~D. (2016),
  The acquisition modes of COSMO-Skymed di Seconda Generazione: A new combined
  approach based on SAR and platform agility, \In\ {\em 2016 IEEE International
  Geoscience and Remote Sensing Symposium (IGARSS)}, pp.~2082--2085.

\bibitem{Mittermayer}
\U Mittermayer,~J., Wollstadt,~S., Prats-Iraola,~P., \and\ Scheiber,~R. (2014),
  The TerraSAR-X Staring Spotlight Mode Concept, {\em IEEE Transactions on
  Geoscience and Remote Sensing}, 52(6), 3695--3706.

\bibitem{Luo2014}
\U {Luo},~Y., {Zhao},~B., {Han},~X., {Wang},~R., {Song},~H., \and\ {Deng},~Y.
  (2014), A Novel High-Order Range Model and Imaging Approach for
  High-Resolution LEO SAR, {\em IEEE Transactions on Geoscience and Remote
  Sensing}, 52(6), 3473--3485.

\bibitem{Meng2018}
\U {Meng},~D., {Ding},~C., {Hu},~D., {Qiu},~X., {Huang},~L., {Han},~B.,
  {Liu},~J., \and\ {Xu},~N. (2018), On the Processing of Very High Resolution
  Spaceborne SAR Data: A Chirp-Modulated Back Projection Approach, {\em IEEE
  Transactions on Geoscience and Remote Sensing}, 56(1), 191--201.

\bibitem{Edelhust2017}
\U {Eldhuset},~K. (2017), High-Resolution Spaceborne SAR Processing Using the
  Decomposed Transfer Function, {\em IEEE Transactions on Aerospace and
  Electronic Systems}, 53(5), 2187--2198.

\bibitem{Zhao2014}
\U {Zhao},~B., {Qi},~X., {Song},~H., {Wang},~R., {Mo},~Y., \and\ {Zheng},~S.
  (2014), An Accurate Range Model Based on the Fourth-Order Doppler Parameters
  for Geosynchronous SAR, {\em IEEE Geoscience and Remote Sensing Letters},
  11(1), 205--209.

\bibitem{Wu2016}
\U {Wu},~Y., {Sun},~G., {Yang},~C., {Yang},~J., {Xing},~M., \and\ {Bao},~Z.
  (2016), Processing of Very High Resolution Spaceborne Sliding Spotlight SAR
  Data Using Velocity Scaling, {\em IEEE Transactions on Geoscience and Remote
  Sensing}, 54(3), 1505--1518.

\bibitem{Wang2015}
\U Wang,~P., Liu,~W., Chen,~J., Niu,~M., \and\ Yang,~W. (2015), A High-Order
  Imaging Algorithm for High-Resolution Spaceborne SAR Based on a Modified
  Equivalent Squint Range Model, {\em IEEE Transactions on Geoscience and
  Remote Sensing}, 53(3), 1225--1235.

\bibitem{RodriguezCassola2019}
\U Rodriguez-Cassola,~M., Prats-Iraola,~P., Krieger,~G., \and\ Moreira,~A.
  (2019), On the use of Time-Domain SAR Focusing in Spaceborne SAR Missions,
  \In\ {\em IGARSS 2019 - 2019 IEEE International Geoscience and Remote Sensing
  Symposium}, pp.~755--758.

\bibitem{Prats2014}
\U {Prats-Iraola},~P., {Scheiber},~R., {Rodriguez-Cassola},~M.,
  {Mittermayer},~J., {Wollstadt},~S., {De Zan},~F., {Bräutigam},~B.,
  {Schwerdt},~M., {Reigber},~A., \and\ {Moreira},~A. (2014), On the Processing
  of Very High Resolution Spaceborne SAR Data, {\em IEEE Transactions on
  Geoscience and Remote Sensing}, 52(10), 6003--6016.

\bibitem{Jakowatz1996}
\U Jakowatz,~C.~V., Wahl,~D.~E., Eichel,~P.~H., Ghiglia,~D.~C., \and\
  Thopmson,~P.~A. (1996), {Spotlight-Mode Synthetic Aperture Radar: A Signal
  Processing Approach}, Boston: Kluwer Academis Publishers.

\bibitem{CalabreseDiego2014}
\U Calabrese,~D. (2014), {DIscrete Stepped Strip (DI2S)}, \In\ {\em {EUSAR
  2014; 10th European Conference on Synthetic Aperture Radar; Proceedings of}},
  pp.~1--4.

\bibitem{SikanetaGierullTGRS2015}
\U Sikaneta,~I. \and\ Gierull,~C. (2015), Phased-Array Beam-Diversity With
  Multiple Channels for Improved SAR Imaging, {\em IEEE Journal of Selected
  Topics in Applied Earth Observations and Remote Sensing}, 8(11), 5106--5115.

\bibitem{Cumming2005}
\U Cumming,~I.~G. \and\ Wong,~F.~H. (2005), {Digital Processing of Synthetic
  Aperture Radar Data: Algorithms and Implementation}, Norwood, MA: Artech
  House Remote Sensing Library.

\bibitem{GebertPHD}
\U Gebert,~N. (2009), {Multi-Channel Azimuth Processing for High-Resolution
  Wide-Swath SAR Imaging}, \phd, University of Karlsruhe.

\bibitem{WoodDiffGeo}
\U Wood,~J., {Notes on the geometry of curves}.
\newblock http://homepages.math.uic.edu/~jwood/analysis/Curvegeomrev.pdf.

\bibitem{Shou2014}
\U Shou,~H.-N. (2014), Orbit Propagation and Determination of Low Earth Orbit
  Satellites, {\em International Journal of Antennas and Propagation}, 2014,
  1--12.

\bibitem{NASAEGM86}
\U NASA, {EGM96, The NASA GSFC and NIMA Joint Geopotential Model}.
\newblock https://cddis.nasa.gov/926/egm96/.

\bibitem{Xiaojin2007}
\U S.,~X., Z.,~Y., \and\ Z.,~W. (2007), Effective velocity estimation for
  space-borne SAR based on chirp scaling algorithm, \In\ {\em 2007 1st Asian
  and Pacific Conference on Synthetic Aperture Radar}, pp.~427--430.

\bibitem{Wong2000}
\U Wong,~F., Tan,~N.~L., \and\ Yeo,~T.~S. (2000), Effective velocity estimation
  for space-borne SAR, \In\ {\em IGARSS 2000. IEEE 2000 International
  Geoscience and Remote Sensing Symposium. Taking the Pulse of the Planet: The
  Role of Remote Sensing in Managing the Environment. Proceedings (Cat.
  No.00CH37120)}, Vol.~1, pp.~90--92 vol.1.

\bibitem{Liang2017}
\U Liang,~C., Fielding,~E.~J., \and\ Huang,~M.-H. (2017), Estimating Azimuth
  Offset With Double-Difference Interferometric Phase: The Effect of Azimuth FM
  Rate Error in Focusing, {\em IEEE Transactions on Geoscience and Remote
  Sensing}, 55(12), 7018--7031.

\bibitem{PratsIraola2014}
\U {Prats-Iraola},~P., {Scheiber},~R., {Rodriguez-Cassola},~M.,
  {Mittermayer},~J., {Wollstadt},~S., {De Zan},~F., {Bräutigam},~B.,
  {Schwerdt},~M., {Reigber},~A., \and\ {Moreira},~A. (2014), On the Processing
  of Very High Resolution Spaceborne SAR Data, {\em IEEE Transactions on
  Geoscience and Remote Sensing}, 52(10), 6003--6016.

\bibitem{Cumming2003}
\U Cumming,~I., Neo,~Y., \and\ Wong,~F. (2003), {Interpretations of the omega-K
  algorithm and comparisons with other algorithms}, \In\ {\em {Geoscience and
  Remote Sensing Symposium, 2003. IGARSS '03. Proceedings. 2003 IEEE
  International}}, Vol.~3, pp.~1455--1458, Toulouse, France.

\bibitem{Franc99}
\U Franceschetti,~G. \and\ Lanari,~R. (1999), {Synthetic Aperture Radar
  Processing}, Washington: CRC Press.

\bibitem{Raney1992}
\U Raney,~R.~K. (1992), A New And Fundamental Fourier Transform Pair, \In\ {\em
  Geoscience and Remote Sensing Symposium, 1992. IGARSS '92. International},
  Vol.~1, pp.~106--107, Houston, TX, USA.

\bibitem{Bamler1992}
\U Bamler,~R. (1992), {A comparison of range-Doppler and wavenumber domain SAR
  focusing algorithms}, {\em Geoscience and Remote Sensing, IEEE Transactions
  on}, 30(4), 706--713.

\bibitem{EnderSignalTheoretic}
\U Ender,~J. H.~G. (2003), {Signal theoretical aspects of bistatic SAR}, \In\
  {\em {Geoscience and Remote Sensing Symposium, 2003. IGARSS '03. Proceedings.
  2003 IEEE International}}, Vol.~3, pp.~1438--1441, Toulouse, France.

\bibitem{Spiegel1964}
\U Spiegel,~M.~R. (1964), {Theory and Problems of Complex Variables}, New York:
  Schaums.

\bibitem{Cafforio1991a}
\U Cafforio,~C., Prati,~C., \and\ Rocca,~F. (1991), {SAR data focusing using
  seismic migration techniques}, {\em Aerospace and Electronic Systems, IEEE
  Transactions on}, 27(2), 194--207.

\bibitem{Sikaneta2014}
\U Sikaneta,~I., Gierull,~C., \and\ Cerutti-Maori,~D. (2014), {Optimum Signal
  Processing for Multichannel SAR: With Application to High-Resolution
  Wide-Swath Imaging}, {\em Geoscience and Remote Sensing, IEEE Transactions
  on}, 52(10), 6095--6109.

\bibitem{NovelRadar}
\U Sikaneta,~I.~C. \and\ Cerutti-Maori,~D. (2017), Novel Radar Techniques and
  Applications, Ch.~{High-resolution wide-swath SAR}, Raleigh: SciTech
  Publishing.

\bibitem{Krieger2004}
\U Krieger,~G., Gebert,~N., \and\ Moreira,~A. (2004), {Unambiguous SAR signal
  reconstruction from nonuniform displaced phase center sampling}, {\em
  Geoscience and Remote Sensing Letters, IEEE}, 1(4), 260--264.

\bibitem{Gebert2009b}
\U Gebert,~N. \and\ Krieger,~G. (2009), {Azimuth Phase Center Adaptation on
  Transmit for High-Resolution Wide-Swath SAR Imaging}, {\em Geoscience and
  Remote Sensing Letters, IEEE}, 6(4), 782--786.

\bibitem{Skolnik}
\U Skolnik,~M. (1990), {Radar Handbook}, McGraw-Hill Professional.

\bibitem{SikanetaCeruttiKlareGierullIGARSS2014}
\U Sikaneta,~I., Cerutti-Maori,~D., Klare,~J., \and\ Gierull,~C. (2014),
  Comparison of multi-channel high-resolution wide-swath SAR processing
  methods, \In\ {\em 2014 IEEE Geoscience and Remote Sensing Symposium},
  pp.~3834--3837.

\bibitem{Cerutti-Maori2010b}
\U Cerutti-Maori,~D., Gierull,~C., \and\ Ender,~J. (2010), {Experimental
  Verification of SAR-GMTI Improvement Through Antenna Switching}, {\em
  Geoscience and Remote Sensing, IEEE Transactions on}, 48(4), 2066--2075.

\bibitem{Gierull2012}
\U Gierull,~C.~H., Sikaneta,~I., \and\ Cerutti-Maori,~D. (2012), {Two-Step
  Detector for RADARSAT-2's Experimental GMTI Mode}, {\em Geoscience and Remote
  Sensing, IEEE Transactions on}, PP(99), 1--19.

\bibitem{Chiu2004}
\U Chiu,~S. \and\ Sikaneta,~I.~C. (2004), {Applying fractional {F}ourier
  transfrom to two-aperture {SAR-GMTI}}, {\em Proc. 2004 EuSAR conf.}

\end{thebibliography}







 
% Add some annexes
\appendix
\input{vectorcalc}
\input{inertialtoecef}
\input{rateofacceleration}
\input{rangeAppendix}
\input{stationaryIteration}
\input{stolz}
\input{mimo}
\input{antennaanglesAppendix}

% Make the DCD sheet
\docctl

% Add the back cover
%\makebackcover

% Write the abstract and significance statement to sr-example.rtf
%\RTFabstract

% Make a partially completed DCGER
%\DCGER{DCGER-template-2015-06-23.rtf}

% Make a CSV file to help fill in the submission form.
%\submission{Submission-template.csv}
\end{document}
